\chapter{INTRODUCTION}

\section{Context of Study}

Network demands for video-conferencing and other high-bandwidth technology is becoming more complex, as well as the network infrastructure that support these demands. For this reason, it is important to develop and test good Quality of Service (QoS) methods, not only in model, typical networks but also in real-life networks. QoS refers to technology that guarantee high-quality provision of resource-intensive, high-priority services \cite{noauthor_what_nodate}. Requirements of QoS are enforced through queuing, which is the ordering of packets in traffic flow, and bandwidth control, which is how much of the network resources the packets take up \cite{zhao_internet_2000}. In traditional networks with disparate forwarding devices with different configurations, queuing and bandwidth control is enforced through service-level agreements between the user and the network provider \cite{karakus_quality_2017}. This does not allow for abstract and fine-grained control of network traffic.

Software-defined networking (SDN) is an emerging network architecture that solves the problem of fragmented network management and configuration by decoupling the data plane from the control plane \cite{kreutz_software-defined_2015}. Forwarding devices in the network are logically centralized, and uses a protocol such as OpenFlow to control behavior. Software-defined networking allows for QoS provisioning to be implemented with a more abstract view of the network, allowing for better control of different types of traffic. Advantages of the SDN paradigm in providing SDN include custom routing of QoS traffic instead of shortest-path routing, better QoE through additional parameters to the traditional QoS metrics, and better monitoring of network dynamics.

Researchers have tested many QoS algorithms on Mininet, which simulates software-defined networks, with a network operating system such as Ryu and OpenFloodLight \cite{karakus_quality_2017}. Regencia and Yu built a testing framework with Mininet and Ryu to test various QoS algorithms under different network topologies \cite{yang_introducing_2022}. However, the study did not investigate the performance of those QoS algorithms in different topologies. The QoS algorithms can be more thoroughly tested with real-world data from the Internet Topology Zoo (ITZ) \cite{knight_internet_2011}, which provides data from network operators about live networks that provide Internet service. This testing is important so that the characteristics of the performance of the different algorithms to understand which are the most optimal in real-world network use cases. It also take full advantage of the flexibility of configuration brought by Software-defined networks, which allow control of the nodes and switches in the network without the constraints of hardware-bound firmware control of traditional networks. Note that there are other networking use cases such as QoE and security that can be applied to this framework of testing, especially with different topologies.

\section{Research Objectives}
The main objective of this study is to analyze Class-based QoS algorithm performance in various network topologies. To achieve this, we modified the aforementioned framework which has been written to generalize layers in a fat-tree topology to generalize for a general graph topology. In that process, we expect to find some differences in network behavior and they can be quantified. Hence, we have the following specific objectives:

\begin{enumerate}
    \item Modify the framework by Regencia and Yu to easily simulate various network topologies and QoS algorithms in those topologies,
    \item Analyze performance of QoS Techniques in different network topology with synthetic traffic load,
    \item And find differences in behavior of the different network topologies, quantify them, and resolve issues that might arise from those differences.
\end{enumerate}

\section{Research Questions}
In this study, we investigate the performance of QoS provisioning algorithms over different network topologies, especially in live network topologies from the ITZ. We aim to answer the following questions:

\begin{enumerate}
    \item How well do Class-based Queuing QoS techniques perform under different network topologies?
    \item What are the differences in the performance characteristics of the different QoS techniques?
    \item Which QoS techniques exhibit the best performance in the different network topology tested?
\end{enumerate}

These research questions were modified since the start of this study, for the reason that the analysis of core-enforced queuing versus leaf-enforced queuing was not completed during the period given for this study.

\section{Scope and Limitations of the Study}

We test the following topologies in the research:
\begin{itemize}
    \item Fat tree with fanout of 3 and 2 layers,
    \item Complete mesh network with 5 Openflow switches,
    \item Networks from data provided by the Internet Topology Zoo.
\end{itemize}

For networks from data provided by the Internet Topology Zoo, We select regional and country-level data with at most 40 nodes to ensure that we have sufficient computing resources for the simulation under the heavy synthetic simulations that will be maintained from the previous study. Only 110 topologies with 40 nodes or less, out of 212 regional/country-level data from the dataset. 

Only the topology connecting the clients was from the study by Regencia and Yu. The network traffic tested will be HTTP requests for images and PDF files, and video-on-demand through the VLC Media Player RTSP servers and clients.
    
We also limited the tested QoS algorithms to the following:
\begin{itemize}
    \item Basic Class-Based Queuing, leaf-enforced
    \item Source Class-Based Queuing, leaf-enforced
\end{itemize}

In testing the topology from the Internet Topology Zoo, we assume that all connections are the same, because metadata on the links between the nodes are not present for all nodes.

\section{Significance of the Study}

This is an extension of the framework introduced by Regencia and Yu in testing QoS algorithms. Since network infrastructure is varied across different places and applications, testing QoS provisioning techniques over various topology will provide better insight to how the techniques perform in real-life contexts. Results of this research can further enable research into finding better QoS routing and queuing techniques by identifying the characteristics of each technique over different topologies. The framework for analyzing various network topologies can be further used in network design and testing new algorithms. Finally, the research will allow network providers to implement better techniques for QoS in providing resource-intensive and critical network traffic such as video conferencing and video-on-demand.

