\chapter{CONCLUSION}
\section{Conclusions}

We were able to modify the testing framework to properly accomodate different topologies through the use of the NetworkX library and a simple modification to the Ryu Controller switch algorithm which incorporates the Spanning-Tree Protocol. We were able to demonstate the functionality of this algorithm with the simulation experiments.

From the results we have the following conclusions:
\begin{enumerate}
    \item For round trip times, the two topologies showed similar results. 
    \item For HTTP file transfer performance, while Basic CBQ was more reliable, with little to no failed requests, raw file transfer rate was higher for Source CBQ in some topologies. 
    \item For HTTP file transfer performance, smaller topologies in cluster 2 performed better under Source CBQ ($24.5\%-27.2\%$), while larger topologies in cluster 1 and 3 performed better under Basic CBQ ($7.74\%-55.568\%$). Cluster 0, which represented the middle-sized topologies in the experiment, had mixed results.
    \item In Source CBQ, the difference of performance between the different clusters was more pronounced in the two benchmarks, while in Basic CBQ, the trend of increasing performance when moving to smaller-sized clusters was less clear.
    \item The performance deficit of Source CBQ compared to Basic CBQ was larger in clusters with large topologies than in clusters with small topologies.
    \item The Basic CBQ was able to provide for better service in video traffic, which was the priority traffic in the experiment.
    \item Overall, Basic CBQ outperformed Source CBQ in the random sample of ITZ network topologies, as well as the two model topologies selected for testing. 
\end{enumerate}
Regarding point 4, this implies that Basic CBQ was more consistent across all topologies in the video streaming benchmark, which means that Basic CBQ exhibited better performance than Source CBQ.

\section{Recommendations}
The following improvements to this research can be implemented to better understand the behavior of the QoS algorithms in different networks.
\begin{enumerate}
    \item Increase the number of servers and the variety of traffic
    \item Investigate algorithms aside from Basic CBQ and Source CBQ, and investigate the differences between leaf-enforced and source-enforced algorithms
    \item Incorporate PCAP into this research to simulate real-life traffic better
    \item Increase the scale, both in the size of the network and the number of clients
    \item Use different path-resolution algorithms other than STP
    \item Investigate the effect of graph structure and shape, while controlling for the number of nodes.
\end{enumerate}
Further comparisons of key performance indicators such as transfer rate and demux bitrate indicate a need for more testing to validate these results and isolate certain variables such as network size, structure, and the choice of path-resolution algorithms. We also recommend that the framework be further improved so that configuration becomes simpler and more consistent (e.g. using a unified data format for storing configuration files).
